### 2016-01-26 paper.tex
Initial Committ

\begin{abstract}
As electronic devices get increasingly personalized,
mixed signal integrated circuits such as analog to digital converters (ADCs)
and digital to analog converters (DACs) play a pivotal role in interfacing 
between the real world and the digital domain. Side-by-side, the security
requirements of these devices are increasing manifold. Many of these devices
require to be authenticated and have built in techniques to support 
encryption and prevent counterfeiting. For embedded devices, 
these requirements are efficiently implemented by 
using physically unclonable functions (or PUFs) that make use of the 
unique nanoscale variations during device fabrication.

In this paper, we show how mixed signal ICs in a device like ADCs and DACs 
have properties that make them amicable for use in PUF applications. By
virtue of having analog components, the PUF properties in these ICs
are significantly more amplified compared to digital PUFs such as those based on
SRAM and ring oscillators. An added advantage is that mixed signal PUFs
have considerably less overheads compared to the contemporary digital PUFs. 
\end{abstract}

\section{Introduction}
The physical characteristics of every electronic device is unique.
The uniqueness is due to micro and nanoscale variations in the 
silicon substrate and fabrication process. A physically unclonable function 
(or PUF) uses this uniqueness to provide a cryptographic key that 
cannot be forged. PUFs have wide application, especially for device
authentication, anti-counterfeiting, and tamper resistance.
Unlike contemporary techniques of storing keys in memory,
PUFs utilize a series of challenges and responses. Each response is a 
function of the challenge and device characteristics.

Several PUFs have been constructed over the years. Most of them
from electronic components such as the SRAM, ring oscillators, flip flops,
FPGA units etc. A few non-electronic PUFs such as optical, acoustic,
and magnetic PUFs have also been proposed. The important requirements
for a PUF is that they should be compact, unforgeable, unpredictable, irreversible, 
reliable, and easy to evaluate. These requirements are easier said than done.
Many of the requirements are contrasting, while many are drastically affected
by noise and other environmental factors such as the ambient temperature.
Thus the search for the search for the perfect PUF is an open problem
and active area of research.

These requirements should be met 
irrespective of the noise and other environmental factors.

In this demonstrate, we hope to build a PUF based on analog to digital
converters (ADCs). These devices are widely used in wireless sensor nodes
and also integrated into many low cost micro-controllers.
Compared to other electronic PUFs, ADC PUFs may not require any 
special hardware such as oscillators, arbiters, etc. They would thus
be compact. The plan is to feed analog waveforms to the ADC (challenges) 
under varying conditions and collect the converted digital outputs 
(responses). The responses would then be analyzed for PUF properties 
such as reproducibility, uniqueness, unclonability, unpredictability, 
one-wayness, etc.

%\bibliographystyle{abbrv}
%\bibliography{screfs}

\section{Background}
A

can be thought as an electronic fingerprint for devices where identification of fingerprints is easy but cloning is very
difficult.

PUF relies on the fact that given the exact details of the manufacturing process, two devices tend to exhibit
different behaviour because of the difference in their physical microstructure. The difference in behaviour should
be difficult to predict but easy to reproduce. PUF uses concept of challenge and response where challenge is the
input applied to the device and response is the value obtained from the device after some post-processing. We
define the challenge response mapping( f ) as follows
f : C → R | f (c) = r c ∈ C and r ∈ R
(1)
where C denotes the domain of challenges and R denotes the range of responses.
The ideal properties for the challenge response function are
1) Evaluatable: The response r ∈ R for a challenge should be easily computed from f and a given challenge
c ∈ C .
2) Unique: the challenge response function( f ) should be unique for each device which will help in identifying
the device.
3) Reproducible: f should be easily reproducible allowing a small degree of error.
4) Unclonable: Given a f it should be virtually impossible to create a cloned function g = f where f (c) ≈ g(c) .3
5) Unpredictable: Given a set of challenge, response pairs P = {(c i , ri)|r i = f (c i )} it should be difficult to
predict response r j for a known challenge c j where r j = f (c j ) and c j ∈
/ P
6) One way: f should be an one way function such that given a response r and f it should be difficult to find
a challenge c such that r = f (c) .

\section{Related Works}
In the last decade various types of PUFs have been proposed. These include non-electronic PUFs like Optical PUFs, Acoustic PUFs, Magnetic PUFs and electronic PUFs. The electronic PUFs can be further subdivided into analog electronic PUFs and digital intrinsic PUFs. The various types of PUFs are discussed in more detail in this section.
\subsection{Non-electronic PUFs}
In non-electronic PUFs, randomness arise due to non electronic components. In the case of \textit{Optical PUFs}, the main component is an optical token which is doped with refractive glass spheres in a random fashion. When the token is radiated with a laser, a speckle pattern is formed. The responses are  unique because  of the microscopic differences between any two tokens. For \textit{Acoustic PUFs}, the main component is an acosutic delay line where an electrical signal is converted to mechanical vibration which is again converted to electrical signal using transducers. The mechanical vibration causes a sound wave and scatters yielding unique reflections. The disadvantage of the above PUFs is that expensive hardware and accurate positioning is required for their construction.
\subsection{Analog electronic PUFs}
In the above classification of PUFs, electronic quantities like capacitance or resistance is measured. An example of such a PUF is \textit{Coating PUF} where randomness of capacitance of a protective coating of comb shaped metal wires on top of an IC is considered. This randomness is induced by a dielectric coating between the metal wires. The advantage of above PUFs is their low cost of construction and the protective coating can be used to detect tampering. However these coating PUFs are not preferred because of the limited challenge response pairs.

\subsection{Digital Intrinsic PUFs}
The PUFs seen so far are non intrinsic PUFs where randomness is explicitly introduced like an optical token in case of Optical PUFs. In intrinsic PUFs, the challenge response collection mechanism is embedded in the device. The intrinsic PUFs can be further subdivided into delay-based PUFs or memory-based PUFs. In delay-based PUFs, randomness in delays of wires and gates are exploited. Commonly used delay-based PUFs are  arbiter PUFs and ring oscillator PUFs. In memory-based PUFs, randomness in settling of values in memory cells is exploited. These include SRAM PUFs, Butterfly PUFs and Flip-flop PUFs.

%Disadvantage of intrinsic puf and why our model is better.
\section{ADC and DAC}
A Digital to Analog Converter(DAC) as the name suggests converts digital data to an analog quantity like voltage. A n-bit DAC can be constructed easily using a R-2R ladder which consists of n R-2R networks. Each network is fed with a reference voltage(say $V_{ref}$) for a set bit or zero voltage for a 0 bit. A R-2R network in the ladder causes the voltage to be split accordingly to its bit position. For a n-bit DAC, output voltage varies from 0 to $(1-\frac{1}{2^{n}})*V_{ref}$ in steps of $\frac{1}{2^{n}}*V_{ref}$. A R-2R DAC suffers from thermal noise which increases with resistance and temperature. The PUF output variation can occur because of microscopic variations in the resistors and switches used.

An Analog to Digital Converter (ADC) on the other hand converts an analog quantity(usually voltage) to its equivalent digital data(usually its amplitude). The prominent ADC types used are
\begin{itemize}
\item \textit{Flash ADC:} Typical flash ADC's consists of voltage ladder of resistors or capacitors paired with comparators which compare input voltage to reference voltage. The output from the comparators passes to an encoder which outputs a binary value. A flash ADC is extremely fast and accurate, but is expensive as $2^{n}-1$ comparators are required for a $n$-bit conversion.
\item \textit{Sigma-Delta ADC:} A sigma-delta ADC consists of modulator and a digital filter. An analog signal is fed to the modulator whose output is fed to the digital filter to obtain the digital output. A sigma-delta DAC achieves high levels of accuracy without using expensive components. However the conversion time is slow compared to other types of ADC's.
\item \textit{Successive-Approximation ADC:} A successive-approximation ADC uses binary search to compare the input signal with varying voltage levels to obtain its equivalent digital output. In SA-ADC, a successive approximation register(SAR) containing a digital value is fed to an internal DAC and its output is compared to the input voltage. A sample and hold(SAH) circuit is used to supply constant input voltage to the comparator. A SA-ADC provides medium levels of accuracy and conversion time. The PUF output variation can occur because of microscopic variations in electrical components used in SAH circuit and internal DAC.
%It suffers from thermal noise for capacitors($kT/C$) which increases with temperature and is inversely proportional to the capacitance. However with higher capacitance, power consumption increases and accuracy decreases and usually a trade off is required.

\end{itemize}

\section{Mixed Circuit based PUF}

\section{Evaluation}

\section{Conclusion}

### 2016-01-28 paper.tex
Image for SA-ADC
R-2R DAC correction
Mixed circuit PUF changes

@@
 The PUF output variation can occur because of microscopic variations in the resistors and switches used.
+\begin{figure}[H]
+\includegraphics[scale=0.8]{SA-ADC.png}
+\centering
+\caption{Block diagram of a 4-bit R-2R DAC}
+\end{figure}
 
@@
 \section{Mixed Circuit based PUF}
+In any electronic device, we encounter conversions from analog form to digital form and vice versa. Consider
+two people speaking through a mobile phone. Sound is converted to an analog signal by the microphone, which is
+then converted to digital form by an analog to digital converter(ADC) for transmission. In the other end, the digital
+data is converted to analog by a digital to analog converter(DAC) and the speaker converts to audible sound. In this
+digitalizing world, ADC and DAC modules are omnipresent in all devices. The main reason behind this is that all the input from
+the external world is analog in nature and the device process everything digitally. This factor plays a key role in
+the idea of using ADC and DAC components for PUFs. The ADC and DAC modules can be embedded inside the chip or outside the chip.
+
+A set of hexadecimal values is passed to the DAC which converts it to its corresponding analog values which is again fed to ADC which converts back to digital value.
+So our challenge is an array of digital values which is fed to the DAC and response is calculated from the digital values output by the ADC of the device.The microscopic variations present in the ADC and DAC components gives rise to an unique response for each device for the same set of challenges.
+This mixed circuit based PUF is cost effective and very efficient as it does not require expensive hardware like arbiters and oscillators for digital electronic PUFs and can be easily reproducible unlike non electronic PUFs.
+Moreover, ADC and DAC components are ubiquitous in modern digital devices and can be modified easily with little effort and integrated effortlessly into the current crop of devices.
 

### 2016-02-04 paper.tex
Added Makefile. Restructured Background, Added figure, and a few more changes

@@
 authentication, anti-counterfeiting, and tamper resistance.
-Unlike contemporary techniques of storing keys in memory,
-PUFs utilize a series of challenges and responses. Each response is a 
-function of the challenge and device characteristics.
 
@@
 and magnetic PUFs have also been proposed. The important requirements
-for a PUF is that they should be compact, unforgeable, unpredictable, irreversible, 
-reliable, and easy to evaluate. These requirements are easier said than done.
-Many of the requirements are contrasting, while many are drastically affected
-by noise and other environmental factors such as the ambient temperature.
-Thus the search for the search for the perfect PUF is an open problem
-and active area of research.
+for a PUF is that they should be compact, unforgeable, unpredictable, 
+irreversible, reliable, and easy to evaluate. These requirements are 
+easier said than met. Many of the requirements are contrasting, while 
+many are drastically affected by noise and other environmental factors 
+such as the ambient temperature. Thus the search for the search for 
+the perfect PUF is an open problem and active area of research.
 
-These requirements should be met 
-irrespective of the noise and other environmental factors.
+We propose to construct PUFs using mixed-signal components such as {\em analog to
+digital converters} (ADCs) and {\em digital to analog converters} (DACs).
+As their names suggest, ADCs convert analog voltage signals 
+to equivalent digital data, while DACs convert digital data into the corresponding
+analog voltage. These devices are omnipresent in embedded 
+systems such as mobile phones, wireless sensor nodes, smart tablets, etc.
+and are often integrated into micro-controllers~\cite{xxx}. 
+In mobile phones for instance, DACs are used to sample audio signals and convert
+them into the digital domain, while ADCs to drive the phone's speaker.
 
-In this demonstrate, we hope to build a PUF based on analog to digital
-converters (ADCs). These devices are widely used in wireless sensor nodes
-and also integrated into many low cost micro-controllers.
-Compared to other electronic PUFs, ADC PUFs may not require any 
-special hardware such as oscillators, arbiters, etc. They would thus
-be compact. The plan is to feed analog waveforms to the ADC (challenges) 
-under varying conditions and collect the converted digital outputs 
-(responses). The responses would then be analyzed for PUF properties 
-such as reproducibility, uniqueness, unclonability, unpredictability, 
-one-wayness, etc.
+Both ADCs and DACs have analog as well as digital parts. This is
+appealing for constructing PUFs due to the following reasons.
+\begin{itemize}
+\item As ADCs and DACs have digital parts that are interfaced with the
+processor, the resulting PUFs built from them are intrensic and  
+directly accessible by applications running in the system. No external 
+measuring equipment is required.
+
+\item By virtue of having analog components in mixed-signal devices, 
+micro and nano scale variations are likely to be observed in two dimensions : 
+device delays and voltage levels. Compare this with the contemporary intrensic
+PUFs, where the variations are only in one dimension; either in the delays or
+the voltage level. For instance, in delay based PUFs like the arbiter and the 
+ring oscillator PUF, inherient differences
+only in delays are captured. On the other hand in memory based PUFs, memories 
+cells settling to either 0 or 1 is captured. In comparison, there are multiple 
+values an analog voltage can take.
+
+\item MS-PUFs do not require any dedicated circuits on chip. It reuses ADCs and
+DACs that are present in the microprocessor. Thus MS-PUFs do not have any overheads.
+\end{itemize}
+
+\begin{figure}[!b]
+\centering
+\caption{Mixed-Signal PUF in a Micro-controller with built-in ADC and DAC. }
+\includegraphics[width=6cm]{figs/mspuf}
+\end{figure}
+
+The scheme for the MS-PUF is shown in Figure~\ref{fig:mspuf}. An output of a DAC channel
+is connected to the input of the ADC. A {\em challenge} in the form of a
+digital time-series pattern is transferred to the DAC from the processor. This signal is
+converted to analog at the DAC's output. The ADC quantifies and reconverts the signal 
+into a time-series digital pattern. This ADC output is the {\em response} to the challenge.
+Since the ADC and DAC are accessible from the processor, a software program can create 
+create a challenge and read the corresponding response. 
+The response is affected by many factors including the quantification and environmental
+noise, and inherient variations due to the fabrication variations of the ADC and the 
+DAC. The latter aspect is the focus for constructing the PUF.
+
+The paper \ldots
+
+The structre of the paper is as follows....
 
@@
 \section{Background}
-A
+\subsection{Physically Unclonable Functions}
+A PUF relies on the fact that two similar devices tend to exhibit
+different behaviour because of differences in their physical microstructure
+and process variations during manufacture. A PUF extracts these differences by a 
+series of challenges and responses. Each response is a 
+function of the challenge and the device characteristics. Thus each device will
+have a different response for the same challenge. A collection of challenge-response pairs
+are used for several cryptographic applications such as device fingerprinting, 
+authentication, anti-cloning, and generation of cryptographic keys.
 
-can be thought as an electronic fingerprint for devices where identification of fingerprints is easy but cloning is very
-difficult.
+The PUF's challenge and response can be represented by a function $f$ 
+mapping the domain of challenges ($\mathcal C$) to a range of responses ($\mathcal R$).
+\begin{equation*}
+f : \mathcal C \rightarrow \mathcal R \,\,\,
+  | \,\,\, f(c) = r, \text{ where } c \in \mathcal C \text{ and } r \in \mathcal R
+\end{equation*}
 
-PUF relies on the fact that given the exact details of the manufacturing process, two devices tend to exhibit
-different behaviour because of the difference in their physical microstructure. The difference in behaviour should
-be difficult to predict but easy to reproduce. PUF uses concept of challenge and response where challenge is the
-input applied to the device and response is the value obtained from the device after some post-processing. We
-define the challenge response mapping( f ) as follows
-f : C → R | f (c) = r c ∈ C and r ∈ R
-(1)
-where C denotes the domain of challenges and R denotes the range of responses.
-The ideal properties for the challenge response function are
-1) Evaluatable: The response r ∈ R for a challenge should be easily computed from f and a given challenge
-c ∈ C .
-2) Unique: the challenge response function( f ) should be unique for each device which will help in identifying
-the device.
-3) Reproducible: f should be easily reproducible allowing a small degree of error.
-4) Unclonable: Given a f it should be virtually impossible to create a cloned function g = f where f (c) ≈ g(c) .3
-5) Unpredictable: Given a set of challenge, response pairs P = {(c i , ri)|r i = f (c i )} it should be difficult to
-predict response r j for a known challenge c j where r j = f (c j ) and c j ∈
-/ P
-6) One way: f should be an one way function such that given a response r and f it should be difficult to find
-a challenge c such that r = f (c) .
+The function $f$ should be one-way, easy to evaluate and reproduce, yet unpredictable
+and unclonable.
 
-\section{Related Works}
-In the last decade various types of PUFs have been proposed.
-These include non-electronic PUFs like Optical PUFs, Acoustic PUFs, Magnetic PUFs and electronic PUFs.
-The electronic PUFs can be further subdivided into analog electronic PUFs and digital intrinsic PUFs.
-The various types of PUFs are discussed in more detail in this section.
-\subsection{Non-electronic PUFs}
-In non-electronic PUFs, randomness arise due to non electronic components.
-In the case of \textit{Optical PUFs}, the main component is an optical token which is doped with refractive glass spheres in a random fashion.
-When the token is radiated with a laser, a speckle pattern is formed.
-The responses are  unique because  of the microscopic differences between any two tokens.
-For \textit{Acoustic PUFs}, the main component is an acosutic delay line where an electrical signal is converted to mechanical vibration which is again converted to electrical signal using transducers.
-The mechanical vibration causes a sound wave and scatters yielding unique reflections.
-The disadvantage of the above PUFs is that expensive hardware and accurate positioning is required for their construction.
-\subsection{Analog electronic PUFs}
-In the above classification of PUFs, electronic quantities like capacitance or resistance is measured.
-An example of such a PUF is \textit{Coating PUF} where randomness of capacitance of a protective coating of comb shaped metal wires on top of an IC is considered.
-This randomness is induced by a dielectric coating between the metal wires.
-The advantage of above PUFs is their low cost of construction and the protective coating can be used to detect tampering.
-However these coating PUFs are not preferred because of the limited challenge response pairs.
+\subsection{Mixed Signal Circuits}
+Mixed signal circuits interface the analog and digital domains in a chip. 
+They are typically used to digitalize real world signals from sensors, which
+then can be processed. Mixed signal circuits are also used to control hardware
+devices. For instance, in a mobile phone, audio signals captured from 
+a microphone are digitalized by means of an {\em analog to digital converter
+(ADC)}, before being processed by the mobile software. Received audio data is
+converted to analog by a {\em digital to analog converter (DAC)} and actuate the
+speakers of the mobile phone. This section provides the necessary background
+for ADCs and DACs.
 
-\subsection{Digital Intrinsic PUFs}
-The PUFs seen so far are non intrinsic PUFs where randomness is explicitly introduced like an optical token in case of Optical PUFs.
-In intrinsic PUFs, the challenge response collection mechanism is embedded in the device.
-The intrinsic PUFs can be further subdivided into delay-based PUFs or memory-based PUFs.
-In delay-based PUFs, randomness in delays of wires and gates are exploited.
-Commonly used delay-based PUFs are  arbiter PUFs and ring oscillator PUFs.
-In memory-based PUFs, randomness in settling of values in memory cells is exploited.
-These include SRAM PUFs, Butterfly PUFs and Flip-flop PUFs.
+An $n$-bit DAC converts and $n$-bit digital value to a corresponding analog
+voltage. A typical DAC uses an R-2R ladder as shown in Figure~\ref{fig:r2r}.
+Each stage comprises of a pair of resistors (R and 2R) and a switch $s_i$ 
+($0 \le i \le n$). The switch $s_i$ is closed only if the $i$-th bit of the
+digital data is one.
 
-%Disadvantage of intrinsic puf and why our model is better.
-\section{ADC and DAC}
-A Digital to Analog Converter(DAC) as the name suggests converts digital data to an analog quantity like voltage.
-A n-bit DAC can be constructed easily using a R-2R ladder which consists of n R-2R networks.
+The current through amplifer is the weighted sum of
+all
+
+can be constructed easily using a R-2R ladder which consists of n R-2R networks.
 Each network is fed with a reference voltage(say $V_{ref}$) for a set bit or zero voltage for a 0 bit.
@@
 However with higher capacitance, power consumption increases and accuracy decreases and usually a trade off is required.
-
 \end{itemize}
 
-\section{Mixed Circuit based PUF}
+\section{Mixed Circuit PUFs}
 In any electronic device, we encounter conversions from analog form to digital form and vice versa. Consider
@@
 
+\section{Related Works}
+In the last decade various types of PUFs have been proposed. The PUFs are categorized into either
+electronic PUFs or non-electronic PUFs. Electronic PUFs are further classified into analog-electronic
+PUFs and digital-intrinsic PUFs. The various types of PUFs are discussed in this section.
+
+\subsection{Non-electronic PUFs}
+As the name suggests, non-electronic PUFs use randomness arising due to non electronic components in the system
+such as from optical, acoustic, and magnetic media. In the case of \textit{Optical PUFs} for instance, the main 
+component is an optical token which is doped with refractive glass spheres in a random fashion. When the token is 
+radiated with a laser, a speckle pattern is formed. The patterns are  unique because  of the microscopic differences 
+between the tokens. In \textit{Acoustic PUFs}, mechanical vibrations is the main source of
+randomness. The vibrations causes a sound wave, which scatters yielding unique reflections. 
+Non-electronic PUFs do not have wide usability due to expensive hardware and accurate positioning 
+required for their construction.
+
+\subsection{Analog electronic PUFs}
+In these PUFs, partial randomness introduced due to electronic quantities like capacitance or 
+resistance is measured. 
+For example, in a \textit{power distribution PUF}, voltage drops based on resistance variations
+in the power grid of a chip is measured. The voltage drops are partial random owing to the
+variations in manufacturing. In a \textit{V\_T PUFs}, differences due to manufacturing variations
+on the threshold voltage of transistors is exploited. In both these PUFs external measuring instruments
+are required, making them expensive.
+
+\subsection{Digital Intrinsic PUFs}
+The PUFs discussed so far are non-intrinsic, where randomness is explicitly introduced into the
+system. In intrinsic PUFs, the challenge response 
+collection mechanism is embedded in the device. There are two types of intrinsic PUFs :
+delay-based and memory-based. In delay-based PUFs, random delays in propagating a current signal
+through wires is exploited. Commonly used delay-based PUFs are arbiter PUFs and ring oscillator 
+PUFs. In memory-based PUFs, randomness in settling of values in memory cells is exploited. 
+These include SRAM PUFs, Butterfly PUFs and Flip-flop PUFs.
+
 \section{Conclusion}

### 2016-02-06 paper.tex
changes to dac and adc in background

@@
 different behaviour because of differences in their physical microstructure
-and process variations during manufacture. A PUF extracts these differences by a 
+and process variations during manufacture. A PUF extracts these 
+differences by a 
 series of challenges and responses. Each response is a 
@@
 Mixed signal circuits interface the analog and digital domains in a chip. 
-They are typically used to digitalize real world signals from sensors, which
-then can be processed. Mixed signal circuits are also used to control hardware
-devices. For instance, in a mobile phone, audio signals captured from 
+They are typically used to digitalize real world signals captured by
+a sensor, which
+can then be processed by software. They are also used to actuate external 
+hardware devices. 
+For instance, in a mobile phone, audio signals captured from 
 a microphone are digitalized by means of an {\em analog to digital converter
@@
 
-An $n$-bit DAC converts and $n$-bit digital value to a corresponding analog
-voltage. A typical DAC uses an R-2R ladder as shown in Figure~\ref{fig:r2r}.
-Each stage comprises of a pair of resistors (R and 2R) and a switch $s_i$ 
+{\flushleft \em Digital to Analog Converters.}
+An $n$-bit DAC converts an $n$-bit digital value into a corresponding analog
+voltage. A typical DAC uses an R-2R network as shown in Figure~\ref{fig:r2r}.
+Each stage in the network comprises of a pair of 
+resistors (R and 2R) and a switch $s_i$ 
 ($0 \le i \le n$). The switch $s_i$ is closed only if the $i$-th bit of the
-digital data is one.
+digital data is one. The resulting voltage at the amplifier's input is the
+sum of voltages due to each closed switch. 
+Each switch contributes a voltage of $\frac{1}{2^{n-i}}$, 
+where $n < i \le 0$. 
+Thus, the analog voltage at the amplifier's input
+is proportional to the digital data.
 
-The current through amplifer is the weighted sum of
-all
-
-can be constructed easily using a R-2R ladder which consists of n R-2R networks.
-Each network is fed with a reference voltage(say $V_{ref}$) for a set bit or zero voltage for a 0 bit.
-A R-2R network in the ladder causes the voltage to be split accordingly to its bit position.
-For a n-bit DAC, output voltage varies from 0 to $(1-\frac{1}{2^{n}})*V_{ref}$ in steps of $\frac{1}{2^{n}}*V_{ref}$.
-A R-2R DAC suffers from thermal noise which increases with resistance and temperature.
-The PUF output variation can occur because of microscopic variations in the resistors and switches used.
-\begin{figure}[H]
-\includegraphics[scale=0.8]{SA-ADC.png}
+\begin{figure}
+\includegraphics[width=6cm]{SA-ADC.png}
 \centering
-\caption{Block diagram of a 4-bit R-2R DAC}
+\caption{Block diagram of a 4-bit R-2R DAC\label{fig:r2r}}
 \end{figure}
 
-An Analog to Digital Converter (ADC) on the other hand converts an analog quantity(usually voltage) to its equivalent digital data(usually its amplitude). The prominent ADC types used are
-\begin{itemize}
-\item \textit{Flash ADC:} Typical flash ADC's consists of voltage ladder of resistors or capacitors paired with comparators which compare input voltage to reference voltage.
-The output from the comparators passes to an encoder which outputs a binary value.
-A flash ADC is extremely fast and accurate, but is expensive as $2^{n}-1$ comparators are required for a $n$-bit conversion.
-\item \textit{Sigma-Delta ADC:} A sigma-delta ADC consists of modulator and a digital filter.
-An analog signal is fed to the modulator whose output is fed to the digital filter to obtain the digital output.
-A sigma-delta DAC achieves high levels of accuracy without using expensive components.
-However the conversion time is slow compared to other types of ADC's.
-\item \textit{Successive-Approximation ADC:} A successive-approximation ADC uses binary search to compare the input signal with varying voltage levels to obtain its equivalent digital output.
-In SA-ADC, a successive approximation register(SAR) containing a digital value is fed to an internal DAC and its output is compared to the input voltage.
-A sample and hold(SAH) circuit is used to supply constant input voltage to the comparator.
+{\flushleft \em Analog to Digital Converters.}
+An $n$-bit ADC converts an analog voltage (or current) to 
+an equivalent $n$-bit digital data. The commonly used ADCs are
+flash, successive-approximation, and sigma-delta ADCs. We give
+a brief background on the successive-approximation ADC; the 
+ADC we used for our expermients.
+
+A successive-approximation ADC {\em SA-ADC} converts an analog
+input to digital using a binary search technique.
+In SA-ADC, a successive approximation register(SAR) containing 
+a digital value is fed to an internal DAC and its output is 
+compared to the input voltage. A sample and hold(SAH) circuit 
+is used to supply constant input voltage to the comparator. 
 A SA-ADC provides medium levels of accuracy and conversion time. 
-The PUF output variation can occur because of microscopic variations in electrical components used in SAH circuit and internal DAC.
+The PUF output variation can occur because of microscopic variations 
+in electrical components used in SAH circuit and internal DAC.
 %It suffers from thermal noise for capacitors($kT/C$) which increases with temperature and is inversely proportional to the capacitance.
 However with higher capacitance, power consumption increases and accuracy decreases and usually a trade off is required.
-\end{itemize}
 
 \section{Mixed Circuit PUFs}
-In any electronic device, we encounter conversions from analog form to digital form and vice versa. Consider
+Nano scale variations in DACs and ADCs.
+
+A R-2R DAC suffers from thermal noise which increases with resistance and temperature. The PUF output variation can occur because of microscopic variations in the resistors and switches used.
+
 two people speaking through a mobile phone. Sound is converted to an analog signal by the microphone, which is

### 2016-02-06 paper.tex
changes in MS-PUF section

@@
 In this paper, we show how mixed signal ICs in a device like ADCs and DACs 
-have properties that make them amicable for use in PUF applications. By
+have properties that make them amicable for use as intrinsic PUFs. By
 virtue of having analog components, the PUF properties in these ICs
-are significantly more amplified compared to digital PUFs such as those based on
+are more stronger compared to digital PUFs such as those based on
 SRAM and ring oscillators. An added advantage is that mixed signal PUFs
@@
 
-\section{Mixed Circuit PUFs}
+\section{Mixed Signal PUFs}
+This section describes how the MS-PUFs are built.
+
+{\flushleft \em Construction of MS-PUF. }
+The MS-PUF is created by connecting an output of a DAC to an
+input channel of an ADC. This creates a loop between the processor
+core, the DAC, and the ADC as shown in Figure~\ref{fig:ms-puf}.
+The sofware generates a challenge in the form of a time-series pattern
+comprising of digital values, which are transferred one at a time
+to the DAC. Each digital value is converted to an analog voltage or
+current and reconverted to a representative digital value by the ADC.
+The software program accumulates 
+all ADC outputs to form the response to the challenge. Algorithm~\ref{algo:puf_sw}
+has the details.
+
+\begin{algorithm}[!ht] \label{algo:puf_sw}
+\begin{scriptsize}
+	\caption{\emph{Software Program for the MS-PUF}}
+	\DontPrintSemicolon
+	\KwIn{$\mathbf C$ : an array representing the challenge}
+	\KwOut{$\mathbf R$ : an array representing the response}
+	\Begin{
+		\For{$i \in \{1, 2, \cdots len(\mathbf C)\}$}{
+			OutputToDAC($\mathbf C_i$); \\
+			/* Wait for ADC to finish conversion */ \;
+			$\mathbf R_i$ = InputfromADC(); \;	
+		}
+		\Return ${\mathbf R}$
+	}
+\end{scriptsize}
+\end{algorithm}
+
+Specify the PUF (formally)
+
+Explain how the analysis is done
+
+Why would we expect to have variation
+
+A DAC output depends on several nano-scale features such 
+as variations in voltage references, resistor tolerances, 
+capacitive effects, and amplifier differences. This could result 
+in two DACs having different responses to the same input. 
+Successive approximation ADCs have a in-built DAC, therefore
+would be affected by the same variations as the DAC. Additionally,
+
+Better PUFs by considering multiple devices
+
+ could cause two DACs to have different responses
+
+ such as the tolerance
+
 Nano scale variations in DACs and ADCs.

### 2016-02-06 paper.tex
modifications in MS-PUF section

@@
 
-{\flushleft \em Construction of MS-PUF. }
+{\flushleft \em Construction of the MS-PUF. }
 The MS-PUF is created by connecting an output of a DAC to an
@@
 core, the DAC, and the ADC as shown in Figure~\ref{fig:ms-puf}.
-The sofware generates a challenge in the form of a time-series pattern
-comprising of digital values, which are transferred one at a time
-to the DAC. Each digital value is converted to an analog voltage or
-current and reconverted to a representative digital value by the ADC.
-The software program accumulates 
-all ADC outputs to form the response to the challenge. Algorithm~\ref{algo:puf_sw}
-has the details.
+The sofware running on the processor core 
+generates a challenge in the form of a time-series pattern
+comprising of $n$-bit digital values, which are transferred one at a time
+to the DAC. Each digital value is converted to an analog voltage (or
+current) and reconverted to a representative $m$-bit digital value by the ADC.
+The software program reads the
+ADC output and forms the response to the challenge using a function $g$.
+Algorithm~\ref{algo:puf_sw} has the details.
 
@@
 		\For{$i \in \{1, 2, \cdots len(\mathbf C)\}$}{
-			OutputToDAC($\mathbf C_i$); \\
+			Output\_to\_DAC($\mathbf C_i$); \\
 			/* Wait for ADC to finish conversion */ \;
-			$\mathbf R_i$ = InputfromADC(); \;	
+			$r$ = Input\_from\_ADC(); \;	
+			$\mathbf R_i = g(C_i, r)$ \;
 		}
@@
 
-Specify the PUF (formally)
-
-Explain how the analysis is done
-
-Why would we expect to have variation
-
-A DAC output depends on several nano-scale features such 
-as variations in voltage references, resistor tolerances, 
+In every iteration in Algorithm~\ref{algo:puf_sw}, $r$, the $m$-bit reply from 
+the ADC is the result of the $n$-bit DAC input $\mathbf C_i$
+undergoing a conversion to analog followed by a reconversion to digital.
+Typically $m$ and $n$ are $8$, $12$, $16$, or $24$ bits. 
+Due to reasons such as quatification and ambient noise, the reply
+$r$ would be different from $\mathbf C_i$. Further, due to nano-scale
+variations between devices, $r$ would vary from one device
+to another.  There are several potential reasons for variations 
+between devices.
+A DAC output for instance, is influenced by several nano-scale features such 
+as voltage references, resistor tolerances, 
 capacitive effects, and amplifier differences. This could result 
 in two DACs having different responses to the same input. 
-Successive approximation ADCs have a in-built DAC, therefore
+Successive approximation ADCs have built in DACs, therefore
 would be affected by the same variations as the DAC. Additionally,
-
-Better PUFs by considering multiple devices
+other components in the ADC such as sample and hold circuits and
+comparators could lead to differences in the reply.
 

### 2016-02-07 paper.tex
R-2R DAC image
Updated caption of R2R dac figure
figure Successive Approx ADC

@@
 \begin{figure}
-\includegraphics[width=6cm]{SA-ADC.png}
+\includegraphics[width=9cm]{R-2R-DAC.png}
 \centering
-\caption{Block diagram of a 4-bit R-2R DAC\label{fig:r2r}}
+\caption{Block diagram of an n-bit R-2R DAC\label{fig:r2r}}
 \end{figure}
@@
 a brief background on the successive-approximation ADC; the 
-ADC we used for our expermients.
+ADC we used for our experiments.
 
@@
 in electrical components used in SAH circuit and internal DAC.
+\begin{figure}[h]
+\includegraphics[width=6cm]{SA-ADC.png}
+\centering
+\caption{Block diagram of an n-bit successive-approximation ADC}
+\end{figure}
 %It suffers from thermal noise for capacitors($kT/C$) which increases with temperature and is inversely proportional to the capacitance.

### 2016-02-08 paper.tex
Modified Section 1 and Section 3. New algorithm for PUF

@@
 systems such as mobile phones, wireless sensor nodes, smart tablets, etc.
-and are often integrated into micro-controllers~\cite{xxx}. 
-In mobile phones for instance, DACs are used to sample audio signals and convert
-them into the digital domain, while ADCs to drive the phone's speaker.
+and are often integrated into micro-controllers~\cite{xxx}. Several 
+micro-controller vendors have multiple DACs and ADCs built into a
+single device.
 
@@
 \centering
-\caption{Mixed-Signal PUF in a Micro-controller with built-in ADC and DAC. }
+\caption{Mixed-Signal PUF in a Micro-controller with built-in ADC and DAC.\label{fig:mspuf} }
 \includegraphics[width=6cm]{figs/mspuf}
@@
 
-The scheme for the MS-PUF is shown in Figure~\ref{fig:mspuf}. An output of a DAC channel
-is connected to the input of the ADC. A {\em challenge} in the form of a
-digital time-series pattern is transferred to the DAC from the processor. This signal is
-converted to analog at the DAC's output. The ADC quantifies and reconverts the signal 
-into a time-series digital pattern. This ADC output is the {\em response} to the challenge.
-Since the ADC and DAC are accessible from the processor, a software program can create 
-create a challenge and read the corresponding response. 
-The response is affected by many factors including the quantification and environmental
-noise, and inherient variations due to the fabrication variations of the ADC and the 
-DAC. The latter aspect is the focus for constructing the PUF.
+The scheme for the MS-PUF is shown in Figure~\ref{fig:mspuf}. Outputs of DACs in the device
+are fedback to the inputs of ADCs to form feedback channels. 
+The DAC in each channel would receive digital data from the processor and convert it
+to an equivalent analog value. The ADC at the other end of the channel would reconvert
+the analog value to a corresponding digital data. The reconverted digital data would 
+be affected by several factors including quantification and environmental noise,
+and inherient variations due to the fabirication of the ADCs and DACs. The latter
+aspect is useful for constructing PUFs.
+
+The PUF {\em challenge} is a 
+digital time-series pattern and a random sequence of feedback channel identifiers. 
+The time-series pattern is transferred to the first channel in the sequence and the 
+and the result read from the corresponding ADC. This result is a time-series 
+digital pattern and is sent to the next channel in the sequence. This `looping' of the
+pattern continues for every channel in the sequence. The result after the final loop
+is taken as the PUFs {\em response}.
 
@@
 
-{\flushleft \em Construction of the MS-PUF. }
-The MS-PUF is created by connecting an output of a DAC to an
-input channel of an ADC. This creates a loop between the processor
-core, the DAC, and the ADC as shown in Figure~\ref{fig:ms-puf}.
-The sofware running on the processor core 
-generates a challenge in the form of a time-series pattern
-comprising of $n$-bit digital values, which are transferred one at a time
-to the DAC. Each digital value is converted to an analog voltage (or
-current) and reconverted to a representative $m$-bit digital value by the ADC.
-The software program reads the
-ADC output and forms the response to the challenge using a function $g$.
-Algorithm~\ref{algo:puf_sw} has the details.
+{\flushleft \em Constructing the MS-PUF. }
+The MS-PUF is created by connecting outputs of DAC to an
+input channel of an ADC. This creates loops between the processors
+cores, DACs, and ADCs as shown in Figure~\ref{fig:ms-puf}.
+If there are $n$ DACs and $m$ ADCs in the device
+(and $n \le m$), then $n$ such loops are made resulting in $n$ feedback channels.
+The PUFs challenge is a time-series pattern comprising of
+$\alpha$-bit digital values and a sequence of random channel identifiers.
+The response is a time-series pattern comprising of $\beta$-bit digital 
+values obtained from the ADC. The values for $\alpha$ and $\beta$ are
+respectively dependent on the DAC and ADC resolutions. Typically, $\alpha = \beta$
+for a device and have values 8, 12, 16, or 24.
+
+Algorithm~\ref{algo:puf_sw} depicts the MS-PUF. 
+The sofware running in the processor core 
+selects the first channel from the sequence ($\mathbf L$) and 
+transfers the time-series digital pattern to the corresponding
+DAC one value at a time ({\em line~5}). Each digital value is converted to an analog voltage (or
+current) and reconverted to a representative digital value by the ADC.
+The software program reads these values from the ADC to form a new digital time-series 
+pattern ({\em line~7}). This pattern forms the input to the next channel in the sequence. The process
+is repeated for the entire sequence. A function $g$ processes the initial pattern ($\mathbf C$) and 
+the final pattern formed (corresponding to $\mathbf L_{len(L)}$) to form the PUFs response.
 
@@
 \begin{scriptsize}
-	\caption{\emph{Software Program for the MS-PUF}}
+	\caption{\emph{MS-PUF : Obtaining the Response to a Challenge}}
 	\DontPrintSemicolon
-	\KwIn{$\mathbf C$ : an array representing the challenge}
+ 	\LinesNumbered
+	\KwIn{$(\mathbf C,\mathbf L)$ : (an array representing digital time-series pattern, 
+                                         a random sequence of channel identifiers)}
 	\KwOut{$\mathbf R$ : an array representing the response}
 	\Begin{
-		\For{$i \in \{1, 2, \cdots len(\mathbf C)\}$}{
-			Output\_to\_DAC($\mathbf C_i$); \\
+		$\mathbf T \leftarrow \mathbf C$ \;
+		\For{$i \in \{1, 2, \cdots, len(\mathbf L)\}$}{
+			\For{$j \in \{1, 2, \cdots, len(\mathbf T)\}$}{
+				Output\_to\_DAC($\mathbf T_j$, $\mathbf L_i$); \\
 				/* Wait for ADC to finish conversion */ \;
-			$r$ = Input\_from\_ADC(); \;	
-			$\mathbf R_i = g(C_i, r)$ \;
+				$r$ = Input\_from\_ADC($\mathbf L_i$); \;	
+				$\mathbf T_j \leftarrow r$ \;
 			}
+		}
+		$\mathbf R \leftarrow g(\mathbf C, \mathbf T)$ \;
 		\Return ${\mathbf R}$
@@
 
-In every iteration in Algorithm~\ref{algo:puf_sw}, $r$, the $m$-bit reply from 
-the ADC is the result of the $n$-bit DAC input $\mathbf C_i$
+In every iteration of Algorithm~\ref{algo:puf_sw}, $r$, the $\beta$-bit 
+reply from the ADC is the result of $\alpha$-bit DAC input $\mathbf T_j$ 
 undergoing a conversion to analog followed by a reconversion to digital. 
-Typically $m$ and $n$ are $8$, $12$, $16$, or $24$ bits. 
-Due to reasons such as quatification and ambient noise, the reply
-$r$ would be different from $\mathbf C_i$. Further, due to nano-scale
-variations between devices, $r$ would vary from one device
-to another.  There are several potential reasons for variations 
+Due to reasons such as quatification and ambient noise, the result ($r$)
+would be different from $\mathbf T_j$ even if $\alpha = \beta$.
+
+Due to nano-scale variations, devices would inject certain randomness into
+$r$ that would depend on the channel used and would vary from one device to another.
+
+There are several potential reasons for variations 
 between devices.
@@
 comparators could lead to differences in the reply.
-
- could cause two DACs to have different responses
-
- such as the tolerance
-
-Nano scale variations in DACs and ADCs.
 

### 2016-02-08 paper.tex
Minor changes in Sec 3

@@
 {\flushleft \em Constructing the MS-PUF. }
-The MS-PUF is created by connecting outputs of DAC to an
-input channel of an ADC. This creates loops between the processors
-cores, DACs, and ADCs as shown in Figure~\ref{fig:ms-puf}.
-If there are $n$ DACs and $m$ ADCs in the device
-(and $n \le m$), then $n$ such loops are made resulting in $n$ feedback channels.
+The MS-PUF is created by connecting outputs of DACs to 
+input channels of an ADC. This creates loops between the processors
+core, DACs, and ADCs as shown in Figure~\ref{fig:ms_puf}.
+If there are $\alpha$ DACs and $\beta$ ADC channels in the device
+(and $\alpha \le \beta$), then $\alpha$ such loops are made resulting 
+in $\alpha$ feedback channels.
 The PUFs challenge is a time-series pattern comprising of
-$\alpha$-bit digital values and a sequence of random channel identifiers.
-The response is a time-series pattern comprising of $\beta$-bit digital 
-values obtained from the ADC. The values for $\alpha$ and $\beta$ are
-respectively dependent on the DAC and ADC resolutions. Typically, $\alpha = \beta$
+$n$-bit digital values and a sequence of random channel identifiers.
+The response is a time-series pattern comprising of $n$-bit digital 
+values obtained from the ADC. The values for $n$ and $m$ are
+respectively dependent on the DAC and ADC resolutions. Typically, $n = m$
 for a device and have values 8, 12, 16, or 24.
@@
 The sofware running in the processor core 
-selects the first channel from the sequence ($\mathbf L$) and 
+selects the first channel from the sequence and 
 transfers the time-series digital pattern to the corresponding
-DAC one value at a time ({\em line~5}). Each digital value is converted to an analog voltage (or
-current) and reconverted to a representative digital value by the ADC.
+channel one value at a time ({\em line~5}). Each input is converted to an analog voltage (or
+current) by the DAC and reconverted to a  digital value by the ADC.
 The software program reads these values from the ADC to form a new digital time-series 
@@
 
-In every iteration of Algorithm~\ref{algo:puf_sw}, $r$, the $\beta$-bit 
-reply from the ADC is the result of $\alpha$-bit DAC input $\mathbf T_j$ 
+In every iteration of Algorithm~\ref{algo:puf_sw}, $r$, the $m$-bit 
+reply from the ADC is the result of the $n$-bit DAC input $\mathbf T_j$ 
 undergoing a conversion to analog followed by a reconversion to digital. 
 Due to reasons such as quatification and ambient noise, the result ($r$)
-would be different from $\mathbf T_j$ even if $\alpha = \beta$.
+would be different from $\mathbf T_j$ even if $m = n$.
 
@@
 $r$ that would depend on the channel used and would vary from one device to another. 
-
-There are several potential reasons for variations 
-between devices.
+There are several potential reasons for variations between channels and devices.
 A DAC output for instance, is influenced by several nano-scale features such 

### 2016-02-08 paper.tex
Minor changes in Sec 3

@@
 
-{\flushleft \em Constructing the MS-PUF. }
+\subsection{Constructing the MS-PUF}
 The MS-PUF is created by connecting outputs of DACs to 
@@
 
+{\flushleft \em Variations in the MS-PUF Response.}
 In every iteration of Algorithm~\ref{algo:puf_sw}, $r$, the $m$-bit 
@@
 
+{\flushleft \em Preventing Modeling Attacks.}
+
+\subsection{A Formal Model for MS-PUFs}
+
+\subsection{xxx}
+
 A R-2R DAC suffers from thermal noise which increases with resistance and temperature. The PUF output variation can occur because of microscopic variations in the resistors and switches used.
-
-two people speaking through a mobile phone. Sound is converted to an analog signal by the microphone, which is
-then converted to digital form by an analog to digital converter(ADC) for transmission. In the other end, the digital
-data is converted to analog by a digital to analog converter(DAC) and the speaker converts to audible sound. In this
-digitalizing world, ADC and DAC modules are omnipresent in all devices. The main reason behind this is that all the input from
-the external world is analog in nature and the device process everything digitally. This factor plays a key role in
-the idea of using ADC and DAC components for PUFs. The ADC and DAC modules can be embedded inside the chip or outside the chip.
-
-A set of hexadecimal values is passed to the DAC which converts it to its corresponding analog values which is again fed to ADC which converts back to digital value.
-So our challenge is an array of digital values which is fed to the DAC and response is calculated from the digital values output by the ADC of the device.The microscopic variations present in the ADC and DAC components gives rise to an unique response for each device for the same set of challenges.
-This mixed circuit based PUF is cost effective and very efficient as it does not require expensive hardware like arbiters and oscillators for digital electronic PUFs and can be easily reproducible unlike non electronic PUFs.
-Moreover, ADC and DAC components are ubiquitous in modern digital devices and can be modified easily with little effort and integrated effortlessly into the current crop of devices.
 

### 2016-04-17 paper.tex
PUF attacks

@@
 
+\section{Attacks on PUFs}
+As more and more security measures arise and evolve, hackers and adversaries come up with new ways to break the security measures.
+Contrary to cryptographic systems which rely on a secret key, PUFs are more secure because of nano scale variations associated with hardware which cannot be cloned even by the manufacturer.
+However they are vulnerable to certain attacks like Fault Attacks, Side-channel attacks and Modelling attacks.
+\subsection {Classification by security}
+Based on the security features, PUFs are classified into
+\begin{itemize}
+\item \textbf{Strong PUFs}\\
+In these PUFs, adversary is given unlimited access and is free to give any number of challenges and obtain its corresponding response. The features of strong PUFs are
+\begin{enumerate}
+\item It is impossible even for the manufacturer to clone the PUF
+\item In a short span of time, it should be hard to obtain all possible challenge-response pairs
+\item It should be impossible to predict response of an unknown challenge, even though the adversary has access to several challenge-response pairs. 
+\end{enumerate}
+
+\item \textbf{Controlled PUFs}\\
+These PUFs add control logic on top of strong PUFs thus limiting access to giving challenges to PUFs and obtaining their corresponding responses.
+They offer some resistance to modelling attacks, even though it is still possible to attack the underlying strong PUF.
+
+\item \textbf{Weak PUFs}\\
+In these PUFs, adversary cannot get the corresponding responses of a known challenge. These PUFs usually have limited number of challenge-response pairs. 
+\end{itemize}
+\subsection {Classification of attacks}
+
+The PUF attacks can be broadly classified into
+\begin{itemize}
+\item \textbf{Fault Attacks}\\ Fault attacks are those attacks which happen when the device is subjected to extreme conditions like temperature.
+This results in unexpected erroneous behaviour which defeats the purpose of device authentication and identification.
+
+\item \textbf{Side-channel Attacks}\\ Side-channel attacks try to extract data based on the physical implementation of the device.
+The adversary studies the behaviour of the device like power consumption, timing information which can reveal further information about the working of the device.
+
+\item \textbf{Modelling Attacks}\\
+The adversary tries to build an mathematical model  from a set of challenge-response pairs.
+From the model, the adversary predicts the response for an unknown challenge with good accuracy.
+So an accurate model can emulate the challenge-response behaviour of a PUF.
+This poses severe vulnerabilities as it would be difficult to distinguish between an actual PUF and some other device emulating the PUF.
+These attacks can be implemented using
+\begin{itemize}
+\item \textit{Lookup Table} based implementation in which we get response from a known challenge which exists in the table.
+The accuracy is pretty high but the drawback is that large number of challenge-response pairs are needed.
+\item \textit{Machine Learning Techniques} such as Support Vector Machines and Logistic Regression which builds an approximate mathematical model which predicts response of an unknown challenge with high probability.
+This can work with significantly lesser number of challenge-response pairs than the Lookup Table bases implementation.
+\subsection{Storage Requirements for Mixed Signal PUF}
+In this section we discuss the storage requirements to correctly predict the response of a challenge using a lookup table.
+Let the mixed signal PUF use a $\beta$ DAC-ADC pair.
+So our challenge is $\beta$ bits.
+Say, the response depends on the previous $\gamma$ challenges and we use $\alpha$ DAC-ADC channels for obtaining the challenge-response pairs.
+\begin{itemize}
+\item Case 1: $\beta$ bit single channel DAC-ADC with no dependence on previous challenges.\\
+In this case, the lookup table will have $2^{\beta}$ entries.
+Each entry will have $\beta$ bit corresponding to the challenge and another $\beta$ bit corresponding to the response.
+So the size of an entry is $2\times\beta$ bits.
+So the total storage required is
+\begin{eqnarray}
+&=& No\ of\ entries\ \times\ Size\ of\ an \ entry  \nonumber \\
+&=& 2^{\beta} \times 2{\beta}\ bits \nonumber \\
+&=& 2^{\beta + 1}\times\beta\ bits.
+\end{eqnarray}
+We can reduce the storage of the lookup table using direct addressing.
+In this case, the entry corresponding to the challenge can be calculated from the index of the lookup table.
+Using this optimization, the size of the entry is $\beta$ bits corresponding to the response and the number of entries remain the same.
+So the total storage required is
+\begin{eqnarray}
+&=& No\ of\ entries\ \times\ Size\ of\ an \ entry  \nonumber\\
+&=& 2^{\beta} \times {\beta}\ bits
+\end{eqnarray}
+
+\item Case 2: $\beta$ bit single channel DAC-ADC with dependence on previous $\gamma$ challenges\\
+In this case, the lookup table will have $2^{\beta\times\gamma}$ entries.
+Each entry will have $\beta*\gamma$ bit corresponding to the challenge and another $\beta$ bit corresponding to the response.
+So size of an entry is $\beta\times(\gamma + 1)$ bits.
+So the total storage required is
+\begin{eqnarray}
+&=& No\ of\ entries\ \times\ Size\ of\ an \ entry  \nonumber \\
+&=& 2^{\beta\gamma} \times \beta\times(\gamma + 1)\ bits 
+%&=& 2^{\beta + 1}*\beta\ bits.
+\end{eqnarray}
+Using direct addressing, the size of an entry can be reduced to $\beta$ bits which is the size of the response avoiding the $\beta*\gamma$ bits required for the challenge.
+So the total storage required is
+\begin{eqnarray}
+&=& No\ of\ entries\ *\ Size\ of\ an \ entry  \nonumber\\
+&=& 2^{\beta\times\gamma} * {\beta}\ bits
+\end{eqnarray}
+
+\item Case 3: $\beta$ bit $\alpha$ channel DAC-ADC with dependence on previous $\gamma$ challenges\\
+Similar to lookup table for a channel with dependence on previous $\gamma$ challenges, we need $\alpha ^ \gamma$ tables which corresponds to the permutation with repetition of previous $\gamma$ challenges coming from  $\alpha-tuple$ set of channels.
+So the storage required is
+\begin{eqnarray}
+&=& \alpha ^ \gamma \times\ Storage\ required\ for \ Case\ 2 \nonumber \\
+&=&  \alpha ^ \gamma \times 2^{\beta\gamma} \times \beta\times(\gamma + 1)\ bits
+\end{eqnarray}
+
+Using direct addressing, we can reduce the storage requirement to $\alpha ^ \gamma \times 2^{\beta\gamma} \times \beta$ bits.
+\end{itemize}
+
+% In the simplest case where the number of channels is one and there is no dependence on previous challenges,
+\end{itemize} 
+\end{itemize}
+
 \section{Related Works}
